Analysis paper

### 2021-06-19 analysis/analysis.Rmd
change plot theme

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)
library(grates)
library(ggdist)

@@

```{r}
dailytruth_data %>%
  dplyr::filter(target_end_date >= min(forecast_dates$full_hub_period), 
                target_end_date <= max(forecast_dates$full_hub_period)) %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_point(size = 0.3, alpha = 0.4) + 
  geom_line(size = 0.5, alpha = 0.4) + 
  geom_line(data = truth_data, aes(y = true_value / 7)) + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  labs(y = "Observed values", x = "Date") + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
                            max(forecast_dates$full_hub_period)))
  theme_light()

@@

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df, ttype = "case") {
  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                   size = 1.7,
                   alpha = 1,
                   position = position_dodge(width = 4)) + 
    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
    #                size = 1.7,
    #                alpha = 0.1,
    #                position = position_dodge(width = 4)) +   
    geom_point(data = unfiltered_data[target_type == ttype], 
               aes(shape = classification)) + 
    geom_line(data = unfiltered_data[target_type == ttype]) + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                            max(forecast_dates$full_hub_period)))
  return(p)
}

@@

# create helper function to plot forecasts -------------------------------------
scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
  p <- scores %>%
  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_light() + 
  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
  theme(legend.position = "bottom") +
  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
  #               xmax = max(forecast_dates$christmas) + 14,
  #               ymin = 0,
  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
  # scale_y_log10() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = FALSE,
  sd = TRUE, 
  quantiles = 0.5
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

  p <- df[grepl(2, target)] %>%
    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
    geom_line() +
    geom_line(aes(y = true_value), color = "black") + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                            max(forecast_dates$full_hub_period))) + 
    labs(y = "Median forecast", x = "Date")
  return(p)
}

@@

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    # geom_density_ridges(aes(fill = model, color = NA),
    #                     rel_min_height = 0.005,
    #                     scale = 0.9,
    #                     # jittered_points = TRUE,
    #                     # position = position_points_jitter(width = 0.05, height = 0),
    #                     point_size = 1.5,
    #                     point_shape = 21,
    #                     #point_shape = '|',
    #                     point_alpha = 1,
    #                     alpha = 0.3) +
    ggdist::stat_slab(alpha = 0.3, scale = 0.8, normalize = "panels") +
  # ggridges::geom_density_ridges(aes(color = NA), scale = 1.3) + 
    ggdist::stat_dots(aes(color = model)) + 
    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
        facet_wrap(~ target_type, ncol = 1, scales = "free") + 
    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
    # geom_density_ridges(quantile_lines=TRUE,
    #                     quantile_fun=function(x,...) mean(x), 
    #                     linetype = "dotted", 
    #                     alpha = 0, 
    #                     scale = 0.9, 
    #                     rel_min_height = 0.01) +
    scale_fill_manual(values = coldeaths) + 
    scale_color_manual(values = coldeaths) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL)) + 
    theme_light()
}

@@

num_fc %>%
  ggplot(aes(x = n_forecasts)) + 
  geom_bar() + 
  theme_light() + 
  labs(x = "Number of available submissions", 
       y = "Number of forecasters")

@@

plot_df %>%
  ggplot(aes(y = scaled_rel_skill, x = n_forecasts)) + 
  geom_point() + 
  geom_line() + 
  theme_light() + 
  facet_wrap(~ target_type) + 
  labs(y = "Scaled relative skill", x = "Number of available submissions") + 
  geom_smooth(method='lm', formula= y~x)

@@

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "mean WIS", x = "Forecast horizon") + 
  theme_light()

@@

# median performance
p_median <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "median WIS", x = "Forecast horizon") + 
  theme_light()

@@

# sd of performance
p_wis_sd <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "WIS - standard deviation", x = "Forecast horizon") + 
  theme_light()

@@

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "sharpness", x = "Forecast horizon") + 
  theme_light()

@@

# absolute error of performance
p_aem <- scores %>%
  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Absolute error", x = "Forecast horizon") + 
  theme_light()

@@

# bias
p_bias <- scores %>%
  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Bias", x = "Forecast horizon") + 
  theme_light()

@@

p_cov50 <- scores[range %in% c(50)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Empirical coverage", x = "Forecast horizon") + 
  theme_light()

@@

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.9, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "empirical coverage", x = "Forecast horizon") + 
  theme_light()

@@

@@

  df[model == m] %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_line() + 
    geom_line(data = d[target_end_date %in% plot_dates],
              aes(y = true_value, x = target_end_date)) +
    geom_line(data = daily[target_end_date >= min(plot_dates) & target_end_date <= max(plot_dates)],
              aes(y = scaled_val, x = target_end_date), alpha = 0.4) +
    geom_vline(aes(xintercept = as.Date(forecast_date), 
                   color = forecast_date), alpha = 0.3, size = 0.4) + 
    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.025`, ymax = `0.975`, 
                                      group = forecast_date, 
                                      fill = forecast_date), alpha = 0.3) +
    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.25`, ymax = `0.75`, 
                                      group = forecast_date, 
                                      fill = forecast_date), alpha = 0.5) +
    ggplot2::geom_line(aes(y = `0.5`,group = forecast_date, 
                           colour = forecast_date), alpha = 1) +
    geom_point() + 
    theme_light() + 
    facet_grid(location_target ~ i, scale = "free_y") + 
    theme(legend.position = "bottom") 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    # scale_y_log10() 
}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)
library(grates)
library(ggdist)
library(ggthemes)

@@

```{r}
dailytruth_data %>%
  dplyr::filter(target_end_date >= min(forecast_dates$full_hub_period), 
                target_end_date <= max(forecast_dates$full_hub_period)) %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_point(size = 0.3, alpha = 0.4) + 
  geom_line(size = 0.5, alpha = 0.4) + 
  geom_line(data = truth_data, aes(y = true_value / 7)) + 
  facet_grid(target_type ~ location_name, scales = "free") + 
  labs(y = "Observed values", x = "Date") + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) - 28, 
                            max(forecast_dates$full_hub_period)))
  theme_minimal()

@@

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df, ttype = "case") {
  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                   size = 1.7,
                   alpha = 1,
                   position = position_dodge(width = 4)) + 
    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
    #                size = 1.7,
    #                alpha = 0.1,
    #                position = position_dodge(width = 4)) +   
    geom_point(data = unfiltered_data[target_type == ttype], 
               aes(shape = classification)) + 
    geom_line(data = unfiltered_data[target_type == ttype]) + 
    theme_minimal() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                            max(forecast_dates$full_hub_period)))
  return(p)
}

@@

# create helper function to plot forecasts -------------------------------------
scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
  p <- scores %>%
  ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_minimal() + 
  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
  theme(legend.position = "bottom") +
  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
  #               xmax = max(forecast_dates$christmas) + 14,
  #               ymin = 0,
  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
  # scale_y_log10() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = FALSE,
  sd = TRUE, 
  quantiles = 0.5) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

  p <- df[grepl(2, target)] %>%
    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
    geom_line() +
    geom_line(aes(y = true_value), color = "black") + 
    theme_minimal() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                            max(forecast_dates$full_hub_period))) + 
    labs(y = "Median forecast", x = "Date")
  return(p)
}

@@

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    # geom_density_ridges(aes(fill = model, color = NA),
    #                     rel_min_height = 0.005,
    #                     scale = 0.9,
    #                     # jittered_points = TRUE,
    #                     # position = position_points_jitter(width = 0.05, height = 0),
    #                     point_size = 1.5,
    #                     point_shape = 21,
    #                     #point_shape = '|',
    #                     point_alpha = 1,
    #                     alpha = 0.3) +
    ggdist::stat_slab(alpha = 0.3, scale = 0.8, normalize = "panels") +
  # ggridges::geom_density_ridges(aes(color = NA), scale = 1.3) + 
    ggdist::stat_dots(aes(color = model)) + 
    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
        facet_wrap(~ target_type, ncol = 1, scales = "free") + 
    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
    # geom_density_ridges(quantile_lines=TRUE,
    #                     quantile_fun=function(x,...) mean(x), 
    #                     linetype = "dotted", 
    #                     alpha = 0, 
    #                     scale = 0.9, 
    #                     rel_min_height = 0.01) +
    scale_fill_manual(values = coldeaths) + 
    scale_color_manual(values = coldeaths) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL)) + 
    theme_minimal()
}

@@

num_fc %>%
  ggplot(aes(x = n_forecasts)) + 
  geom_bar() + 
  theme_minimal() + 
  labs(x = "Number of available submissions", 
       y = "Number of forecasters")

@@

plot_df %>%
  ggplot(aes(y = scaled_rel_skill, x = n_forecasts)) + 
  geom_point() + 
  geom_line() + 
  theme_minimal() + 
  facet_wrap(~ target_type) + 
  labs(y = "Scaled relative skill", x = "Number of available submissions") + 
  geom_smooth(method='lm', formula= y~x)

@@

# mean performance
p_mean <- scores %>%
  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "mean WIS", x = "Forecast horizon")

@@

# median performance
p_median <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_0.5, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "median WIS", x = "Forecast horizon") + 
  theme_minimal()

@@

# sd of performance
p_wis_sd <- scores %>%
  ggplot(aes(x = horizon, y = interval_score_sd, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "WIS - standard deviation", x = "Forecast horizon") + 
  theme_minimal()

@@

# sharpness of performance
p_sharpness <- scores %>%
  ggplot(aes(x = horizon, y = sharpness, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "sharpness", x = "Forecast horizon") + 
  theme_minimal()

@@

# absolute error of performance
p_aem <- scores %>%
  ggplot(aes(x = horizon, y = aem, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Absolute error", x = "Forecast horizon") + 
  theme_minimal()

@@

# bias
p_bias <- scores %>%
  ggplot(aes(x = horizon, y = bias, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "Bias", x = "Forecast horizon") + 
  theme_minimal()

@@

p_cov50 <- scores[range %in% c(50)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  scale_color_manual(values = coldeaths) + 
  labs(y = "Empirical coverage", x = "Forecast horizon") + 
  theme_minimal() + 
  expand_limits(y=c(0, 1)) + 
  theme(legend.position = "bottom") + 
  scale_y_continuous(labels = scales::percent)

@@

p_cov90 <- scores[range %in% c(90)] %>%
  ggplot(aes(x = horizon, y = coverage, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type) + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  geom_hline(yintercept = 0.90, linetype = "dashed") +
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "empirical coverage", x = "Forecast horizon") + 
  expand_limits(y=c(0, 1)) + 
  scale_y_continuous(labels = scales::percent)

@@

```{r}
scores <- eval_forecasts(filtered_data[model %in% 
                                         ensemble_models[!grepl("mean", ensemble_models)]], 
                         summarise_by = c("model", "target_type", "horizon"), 
                         quantiles = 0.5, 
                         sd = TRUE)

# mean performance
p_mean_ens <- scores %>%
  ggplot(aes(x = horizon, y = interval_score, group = model, color = model)) + 
  geom_point() + 
  geom_line() + 
  facet_wrap(~ target_type, scales = "free_y") + 
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  scale_color_manual(values = coldeaths) + 
  labs(y = "mean WIS", x = "Forecast horizon")

``` {r}
scores <- eval_forecasts(filtered_data[model %in% regular_models], 
                         summarise_by = c("model", "target_type", "location", 
                                          "horizon", "forecast_date"))
scores <- scores[order(interval_score), , by = c("target_type", "location", 
                                               "horizon", "forecast_date")]
scores <- scores[, ranking := 1:.N, by = c("target_type", "location", 
                                           "horizon", "forecast_date")]

@@

  df[model == m] %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_line() + 
    geom_line(data = d[target_end_date %in% plot_dates],
              aes(y = true_value, x = target_end_date)) +
    geom_line(data = daily[target_end_date >= min(plot_dates) & target_end_date <= max(plot_dates)],
              aes(y = scaled_val, x = target_end_date), alpha = 0.4) +
    geom_vline(aes(xintercept = as.Date(forecast_date), 
                   color = forecast_date), alpha = 0.3, size = 0.4) + 
    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.025`, ymax = `0.975`, 
                                      group = forecast_date, 
                                      fill = forecast_date), alpha = 0.3) +
    ggplot2::geom_ribbon(ggplot2::aes(ymin = `0.25`, ymax = `0.75`, 
                                      group = forecast_date, 
                                      fill = forecast_date), alpha = 0.5) +
    ggplot2::geom_line(aes(y = `0.5`,group = forecast_date, 
                           colour = forecast_date), alpha = 1) +
    geom_point() + 
    theme_minimal() + 
    facet_grid(location_target ~ i, scale = "free_y") + 
    theme(legend.position = "bottom") 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    # scale_y_log10() 
}
